IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-07-23 main.tex
:pencil: Update parameter description
:pencil: Update parameters
:art: Update font size

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose two BCD algorithms that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

@@

				{\boldsymbol{\Phi}}{\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}

@@

				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}

@@

				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}

@@

				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_gp}}{}

@@

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflected links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}. Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}

>>>>

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose two BCD algorithms that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

@@

				{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}

@@

				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}

@@

				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}

@@

				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}

@@

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflected links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}. Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

				{\scriptstyle{\boldsymbol{\Phi}}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
